---
title: "linear model from Web"
author: "MarenaO"
date: "Spring 2022 Semester"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNG <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNG + geom_point() + geom_lm()
```


### Numerical results

```{r}
cor(ARM~SIMS,data=data)
```

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

#### Predict at target point
```{r}
value = 88 * 0.054563 - 4.095160
print ("The value is, ")
print (value)
```

```{r}
new = data.frame(ARM = 88, GRIP = 94)
```

```{r}
predict(model.1, new, interval = "prediction")
```




#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicNN + geom_point() + geom_lm()
```
  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

The scatterplot for model 2 seems to be going towards uphill to the right, meaning it has a positive correlation.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```


### Inferential  (Build model.2)
  
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

```{r}
newdata<-data_frame(ARM=88, GRIP=94)
```


#### predict model.2 at target point

```{r}
value = 94 * 0.045463 - 4.809675
print ("The value is, ")
print (value)
```

```{r}
predict(model.2,newdata,interval="prediction")
```

#### now add the model fit to our plot for model.2
  
```{r}
basicNG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicNG + geom_point() + geom_lm()
```


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  ARM+GRIP has a better correlation than ARM and GRIP alone (model 2 and model 1).
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

Model 3 seems to be the best model since its residual standard error is the smallest out of the other models, and the smaller it is the better model it is. It also has the greatest adjusted R-squared value out of the other models, and the biggest adjusted R-squared value means that is the better model.

#### predict model.3 at target point
  
```{r}
value = 0.037311 * 0.024470 - 5.433871
print ("The value is, ")
print (value)
```
```{r}
predict(model.2,newdata,interval="prediction")
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```

This shows that the model with ARM (model 1) is better than the model with GRIP (model 2) and the Residual Sum of Squares went down by 25.